---
title: "RWorksheet_Caneso#4b"
author: "Rovel Jan Caneso"
date: "2024-10-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


**1. Using the for loop, create an R script that will display a 5x5 matrix as shown in
Figure 1. It must contain vectorA = [1,2,3,4,5] and a 5 x 5 zero matrix.**
```{r}
vectorA = c(1,2,3,4,5)

matr <- matrix(nrow = 5, ncol = 5)

for(i in 1:5){
  for(j in 1:5){
    matr[i, j] <- vectorA[abs(i-j) + 1]
  }
}

for(i in 1:5){
  for(j in 1:5){
    cat(matr[i,j], " ")
  }
  cat("\n")
}

matri <- matrix(0, nrow = 5, ncol = 5)

for(i in 1:5){
  for(j in 1:5){
    cat(matri[i,j], " ")
  }
  cat("\n")
}
```

**2. Print the string "*" using for() function. The output should be the same as shown
in Figure**
```{r}
for(i in 1:5){
  for(j in 1:i){
    cat("*", " ")
  }
  cat("\n")
}
```

**3. Get an input from the user to print the Fibonacci sequence starting from the 1st input
up to 500. Use repeat and break statements. Write the R Scripts and its output.**
```{r}
#inp <- readline("Enter a number: ")
inp <- 1

f <- 0
s <- 1
repeat{
  if(f >= inp){
    cat(f, " ")
  }
  
  fibona <- f+s
  f <- s
  s <- fibona
  
  if(f > 500) break
}
```

**4. Import the dataset as shown in Figure 1 you have created previously.**
```{r}
#a. What is the R script for importing an excel or a csv file? Display the first 6 rows of
#   the dataset? Show your codes and its result.
shoesize <- read.csv("shoesize_data.csv")
head(shoesize)
#b. Create a subset for gender(female and male). How many observations are there in
#   Male? How about in Female? Write the R scripts and its output.
female <- subset(shoesize, Gender == "F", select = Gender)
female
male <- subset(shoesize, Gender == "M", select = Gender)
male
#c. Create a graph for the number of males and females for Household Data. Use plot(),
#   chart type = barplot. Make sure to place title, legends, and colors. Write the R scripts and
#   its result.
genders <- table(shoesize$Gender)

barplot(genders,
        main = "Number of Females and Males",
        xlab = "Gender",
        ylab = "Count",
        col = c("Pink", "Blue"),
        names.arg = c("Female", "Male"),
        legend = rownames(genders))
```

**5**
```{r}

```

